### 2018-04-26 ident/docs/draft_3.tex
make intro and methods corrections

	The development of these enzyme kinetic rate laws is based on in vitro observations of enzyme activity. Accordingly, authors have questioned their relevance for gleaning information on the dynamics of metabolism under in vivo conditions, as opposed to in vitro conditions \parencite{Heijnen2005,Heijnen2013}. This problem is further compounded by the fact that typical parameter values used in kinetic models of metabolism are estimated in vitro, and may not be applicable under in vivo conditions \parencite{Heijnen2005,Smallbone2007}. Also, parameters estimated based on in vivo experimental data are associated with large uncertainties \parencite{Link2014}. Using in vitro, or unreliable in vivo parameter estimates to study the steady state and dynamic responses of metabolic networks to different perturbations, under in vivo conditions, reduces confidence in the model predicted behaviour. Consequently, this hampers the use of these models to gain insight into metabolic network function \parencite{Andreozzi2016a,Vasilakou2016}, and the increase in prediction uncertainty becomes an obstacle for using the predicted responses as a basis for designing the metabolic networks to achieve any of the aforementioned goals of metabolic engineering and design \parencite{Saa2017}.

	Although some authors have sought to quantify this uncertainty using different techniques \parencite{Vanlier2013,Andreozzi2016a}, others have proposed to alleviate as well as constrain the uncertainty in parameter estimates and consequent model predictions by using a Monte Carlo approach to kinetic modeling of metabolism that allows for integration of experimentally observed in vivo data \parencite{Srinivasan2015}. Bayesian approaches to improve parameter estimation and quantify estimation uncertainty have also been proposed \parencite{Saa2016}.

@@

	In this paper, we propose a scalable methodology that uses available steady state fluxomics, metabolomics and proteomics data to test the practical identifiability of parameters for each individual reaction in kinetic models of metabolism. We demonstrate how the computer algebra-based method that we have developed can also facilitate the design of experiments that are minimal and informative to generate data required to estimate unique parameter values for all reaction fluxes in a metabolic network. In doing so, we not only propose the number and types of perturbations that will provide the most useful data for parameter estimation, but also test the identifiability of different enzyme kinetic rate laws that are typically used to model fluxes in metabolic networks.

	For the purposes of this method we assume that all intracellular metabolite concentrations and fluxes can be measured. We illustrate our methodology to identify parameters and design experiments to identify parameters in a small metabolic network model of glucoeneogenesis in \textit{Escherichia coli} \parencite{Kotte2014, Srinivasan2017}.

@@

	As an example, if 90\% of all the experimental data combinations used for testing can identify a parameter $\theta_i$, then the degree of identifiability of $\theta_i$ is said to be 0.9 or 90\%. On the other hand, if only 50\% of the combinations can identify another parameter $\theta_j$, then $\theta_j$ has a degree of identifiability of 0.5 or 50\%. Furthermore, we can create a hierarchy of practically identifiable parameters using their degrees of identifiability. In the above instance of the two parameters $\theta_i$ and $\theta_j$ that have degrees of identifiability of 90\% and 50\% respectively, $\theta_i$ is classified to be more identifiable than $\theta_j$ due to its relatively higher degree of identifiability.

>>>>

	Despite its importance, the parameterization of kinetic models is still a problem for which solutions are a subject of debate within the modeling community. Typically, enzyme kinetic rate laws are parameterized based on in vitro observations of enzyme activity, as opposed to observations made under in vivo conditions \parencite{Heijnen2005,Smallbone2007}. However, some researchers have questioned their relevance for gleaning information on the dynamics of metabolism under in vivo conditions, as opposed to in vitro conditions \parencite{Heijnen2005,Heijnen2013}. On the other hand, some reports have shown that despite the large uncertainties associated with parameters estimated based on in vivo experimental data \parencite{Link2014}, in vitro parameter estimates are a reasonable approximation of values that would be applicable under in vivo conditions \textcolor{red}{(Ron Milo paper comparing in vitro vs invivo enzyme turn over rates in PLoS Computational Biology)}.

	 Nevertheless, some authors have sought to quantify the uncertainty in in vivo parameter estimates using different techniques \parencite{Vanlier2013,Andreozzi2016a}, while others have proposed to alleviate as well as constrain the uncertainty in parameter estimates and consequent model predictions by using a Monte Carlo approach to kinetic modeling of metabolism. These approaches also allow for the integration of experimentally observed in vivo data. ORACLE \textcolor{red}{(Wang and Haztzimanikatis, 2004)} and Ensemble modeling \textcolor{red}{(Tan and Liao, 2008)} are two examples of such an approach. These and other Monte Carlo kinetic modeling methods have been previously reviewed \parencite{Srinivasan2015}. Bayesian approaches to improve parameter estimation and quantify estimation uncertainty have also been proposed \parencite{Saa2016}.

@@

	In this paper, we propose a scalable methodology that uses available steady state fluxomics, metabolomics and proteomics data to test the practical identifiability of parameters for each individual reaction in kinetic models of metabolism. We demonstrate how the computer algebra-based method that we have developed can also facilitate the design of experiments that are minimal and informative to generate data required to estimate unique parameter values for all reaction fluxes in a metabolic network. In doing so, we not only propose the number and types of perturbations that will provide the most useful data for parameter estimation, but also test the identifiability of different enzyme kinetic rate laws that are typically used to model fluxes in metabolic networks. We illustrate our methodology to identify parameters and design experiments to identify parameters in a small metabolic network model of glucoeneogenesis in \textit{Escherichia coli} \parencite{Kotte2014, Srinivasan2017} under the assumption that all intracellular metabolite concentrations and fluxes can be measured.

@@

	As an example, if 90\% of all the experimental data combinations used for testing can identify a parameter $\theta_i$, then the degree of identifiability of $\theta_i$ is said to be 0.9 or 90\%. On the other hand, if only 10\% of the combinations can identify another parameter $\theta_j$, then $\theta_j$ has a degree of identifiability of 0.1 or 10\%. Furthermore, we can create a hierarchy of practically identifiable parameters using their degrees of identifiability. In the above instance of the two parameters $\theta_i$ and $\theta_j$ that have degrees of identifiability of 90\% and 10\% respectively, $\theta_i$ is classified to be more identifiable than $\theta_j$ due to its relatively higher degree of identifiability.
